\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
% itemize spacing tweaks done inline below
\newenvironment{tightitemize}{\begin{itemize}\setlength\itemsep{0pt}\setlength\parsep{0pt}}{\end{itemize}}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\setlength{\parskip}{0.4em}
\setlength{\parindent}{0pt}
\definecolor{passgreen}{RGB}{0,120,0}
\definecolor{failred}{RGB}{180,0,0}
\definecolor{warnorange}{RGB}{200,100,0}
\newcommand{\code}[1]{\texttt{\small #1}}
\newcommand{\PASS}{\textcolor{passgreen}{\textbf{PASS}}}
\newcommand{\FAIL}{\textcolor{failred}{\textbf{FAIL}}}
\title{FEECM Repository Maintenance Report \\
\large 2026-05-06 to 2026-05-09}
\author{Howard Tu (with Claude Code agent assistance)}
\date{Generated 2026-05-09}
\begin{document}
\maketitle

\section{Why this report exists}

Between 2026-05-06 and 2026-05-09 the \code{feecm/} repository went
through a substantial maintenance pass: branch reconciliation, source
integration of contributions from a long-divergent collaborator branch
(\code{AshokG}), a project-tree restructure, MOOSE-deprecation fixes
across hundreds of input files, and finally the consolidation of the
\code{ec\_beta} app into \code{ecm\_test} so that the former could be
deleted.

This document is a self-contained recall aid: what was done, why,
where the artifacts live, and what remains open.

\section{Top-of-mind: what changed structurally}

\subsection{The four-app layout collapsed to three}

\textbf{Before (start of session):}
\begin{tightitemize}
  \item \code{ec\_beta/} --- electrochemistry-only app
  \item \code{ecm\_test/} --- electro-chemo-mechanics
  \item \code{eel/} --- battery physics from literature (Argonne 2023)
  \item \code{tecm\_test/} --- thermal-electro-chemo-mech, forked from eel
\end{tightitemize}

\textbf{After:}
\begin{tightitemize}
  \item \code{ecm\_test/} --- absorbed all 74 of \code{ec\_beta}'s registered classes; \code{ecm-opt} is now a strict superset of the former \code{ec\_beta-opt}
  \item \code{eel/} --- unchanged scope; gained 5 \code{*Scaled} non-dim materials from Ashok and small revisions to \code{ChargeTransferReaction}/\code{MassDiffusion}
  \item \code{tecm\_test/} --- unchanged scope
  \item \code{ec\_beta/} --- \textbf{deleted} (commit \code{b50b8738})
\end{tightitemize}

\subsection{Project tree rationalized}

Input files (\code{.i}) used to live inside each app under \code{problems/} or \code{examples/}.
The user moved all of them to a top-level \code{projects/} tree to
separate science work from app source. The current layout:

\begin{verbatim}
feecm/
  ecm_test/         <- app
  eel/              <- app
  tecm_test/        <- app
  patchMoose2Feecm/ <- MOOSE framework patches (manual apply)
  doc/              <- repo-wide docs (this report lives here)
  projects/         <- science workspace
    ecmTest/    (43 sub-projects, includes former ecBeta)
    eel/        (13 sub-projects)
    tecmTest/   (3 sub-projects)
    paper_shafee_cathode/
    doc/        <- per-project audit reports
\end{verbatim}

\section{Branch state}

The session worked on two branches:

\begin{tightitemize}
  \item \code{HowardTu} --- the user's working branch. Was 94 commits behind
    \code{origin/master} at session start. Synced via merge commit \code{ee215731}
    on 2026-05-06.
  \item \code{integrate-ashok} --- created off \code{HowardTu} on 2026-05-06 to
    bundle the Ashok integration as a reviewable feature branch. \textbf{Currently
    holds all the session's work}, including the ec\_beta consolidation as the most
    recent commit (\code{b50b8738}).
\end{tightitemize}

\code{integrate-ashok} has not been merged back to \code{HowardTu} yet. The
plan-of-record is \texttt{git merge --no-ff integrate-ashok} into HowardTu when
satisfied, then optionally push.

\section{Chronological narrative}

\subsection{Phase 1: HowardTu $\leftarrow$ master sync (2026-05-06)}

\code{HowardTu} was 94 commits behind \code{origin/master}. Local \code{master}
was also 96 behind. Resolved cleanly:
\begin{tightitemize}
  \item \code{git fetch . origin/master:master} fast-forwarded local master.
  \item \code{git merge --no-ff master} on HowardTu created merge commit \code{ee215731}.
    232 files brought in, no conflicts. New content was mostly under \code{deecm/}
    and \code{feecm/projects/paper\_shafee\_cathode/}.
\end{tightitemize}

\subsection{Phase 2: Ashok integration (2026-05-06)}

\code{AshokG} branch had \textbf{no common ancestor} with master --- root commits
diverged. A normal merge wasn't viable. Approach used: ``diff-and-port'' via a
feature branch \code{integrate-ashok}, with each contribution as its own commit.

The 11 commits on \code{integrate-ashok} (oldest to most recent):

\begin{longtable}{l p{0.55\textwidth}}
\toprule
Commit & What it adds / does \\
\midrule
\endhead
\code{28f140cb} & EEL non-dimensional \code{*Scaled} materials (10 files): ChemicalPotential, MassDiffusion, Migration, BulkChargeTransport, ChargeTransferReaction \\
\code{5a23e98c} & ec\_beta net-new anisotropic-diffusion materials (3 pairs): ADDiffusionAlongPrincipalDirectionsMaterial, AnisotropyMaterialConst, RotatedConductivityTensor \\
\code{52e4ac8b} & ecm\_test PenaltyInterfaceDiffusion (later reverted) \\
\code{df5d9d41} & \code{patchMoose2Feecm/} folder --- MOOSE tensor\_mechanics patches (RZ-coordinate fix for ADComputeFiniteStrain) \\
\code{4a9afc4f} & eel ChargeTransferReaction: Real $\to$ AD-coupled temperature \\
\code{76f6d1bf} & eel MassDiffusion: added \code{phi0}, \code{L0} params for non-dim scaffolding \\
\code{902845e7} & 15 ecm\_test source pairs ported into ec\_beta (using master's current ecm\_test, with ecmApp $\to$ ecBetaApp swap) \\
\code{7d8c1496} & 3 Ashok-only anisotropic auxkernel/kernel pairs to ec\_beta \\
\code{13e66d0a} & \code{projects/ecBeta/ashok\_project/} (94 input/data files for dendrite\_growth + ECM\_benchmark/Ashok\_BenchMark) \\
\code{cd4fba55} & 4 LiB charging inputs (ashok variants + postprocess.py) into projects/eel/LiB/ \\
\code{5c71a4a5} & Drop redundant PenaltyInterfaceDiffusion (MOOSE framework now provides it) \\
\bottomrule
\end{longtable}

\textbf{Verification:} all four apps build cleanly after these commits
(\code{ec\_beta-opt}, \code{ecm-opt}, \code{tecm\_test-opt}, \code{eel-opt}).

\subsection{Phase 3: Project-input audit (2026-05-06)}

Ran \code{--check-input} on every \code{.i} file under \code{projects/}.
Initial result: \textbf{73 PASS / 306 FAIL across 379 inputs in 60
projects.} Failure categories:

\begin{tightitemize}
  \item Missing custom classes (\code{ParamDiffusion}, \code{paperHongli}) --- 29 inputs
  \item Missing \code{.e}/\code{.msh}/\code{.cpa.gz} data files --- ${\sim}70$
  \item MOOSE class drift (\code{ContactDOFSetSize}, \code{NormalNodalLMMechanicalContact}, \code{ADPresetBC}) --- 12
  \item Deprecated input syntax (\code{Problem/coord\_type}, \code{Modules/TensorMechanics/.../use\_displaced\_mesh}, \code{Outputs/out/csv}) --- many
  \item One-off issues
\end{tightitemize}

The full audit details (per-project, per-input failure mode) are in \code{feecm/projects/doc/project\_audit.pdf}.

\subsection{Phase 4: ecBeta repair pass (2026-05-06 -- 2026-05-07)}

Bulk fixes that took ecBeta from 16/76 PASS to 38/76 PASS:

\begin{tightitemize}
  \item \code{paperHongli} (lowercase) $\to$ \code{PaperHongli} (correct case): 15 input files renamed.
  \item Ported \code{ParamDiffusion} (and 10 more classes) from ecm\_test into ec\_beta with \code{ecmApp} $\to$ \code{ecBetaApp} swap.
  \item Enabled \code{CONTACT := yes} in \code{ec\_beta/Makefile}.
  \item Other casing fixes: \code{sourceTerm} $\to$ \code{SourceTerm}, \code{chargeDensity} $\to$ \code{ChargeDensity}, \code{SingleSEInterfaceBV} $\to$ \code{SingleSEInterface}.
  \item Deprecation rewrites: 21 input files had \code{ADDiffusionAlongPrincipalDirections} renamed to \code{*Material}; 15+ files had \code{[Problem]/coord\_type = RZ} relocated to \code{[Mesh]/coord\_type = RZ}; 5+ had \code{use\_displaced\_mesh} removed from TensorMechanics action; CSVs from Exodus output blocks removed.
  \item Mesh regeneration: 3 missing \code{.msh} files generated/copied (\code{mdlR3.msh}, \code{cosine\_conformal.msh}, \code{inclined.msh}).
  \item Custom: \code{test\_circle.i} alpha vector format fix (\code{alpha1/alpha2/alpha3} $\to$ \code{alpha = `0.0 1.0 0.0'}).
\end{tightitemize}

\subsection{Phase 5: ECM\_benchmark $\to$ 23/23 PASS (2026-05-08)}

The \code{ECM\_benchmark} folder Ashok had created in ec\_beta was identical
in structure to ecmTest's flat-named benchmarks. After ecBeta-side fixes,
the user noted Ashok's claim that ``all benchmarks work in EC\_beta'' should
be true. We synced ecBeta's already-fixed versions back to the parallel
ecmTest files (10 files), copied the regenerated \code{cosine\_conformal.msh}
into ecmTest's \code{benchmark2\_freeGrowth/data/}, and confirmed:

\begin{center}
\begin{tabular}{l c c}
\toprule
Sub-project & ecBeta/ECM\_benchmark & ecmTest top-level \\
\midrule
benchmark1\_metalCreep & 1/1 \PASS & 4/4 \PASS \\
benchmark2\_freeGrowth & 11/11 \PASS & 6/6 \PASS \\
benchmark2\_uniformGrowth & 3/3 \PASS & 2/2 \PASS \\
benchmark3\_confinedGrowth & 5/5 \PASS & 5/5 \PASS \\
benchmark3\_growthDiffusion & 1/1 \PASS & --- \\
benchmark4\_fullCoupled & 2/2 \PASS & 2/2 \PASS \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Phase 6: ecmTest repair pass (2026-05-08 -- 2026-05-09)}

Same bulk-fix techniques applied to ecmTest. Result: \textbf{30 PASS $\to$ 126 PASS}.

\begin{tightitemize}
  \item 46 \code{coord\_type} relocations
  \item 24 \code{use\_displaced\_mesh} removals
  \item 20 \code{included\_subdomain\_ids} $\to$ \code{included\_subdomains} (MOOSE rename)
  \item 2 \code{ADPresetBC} $\to$ \code{ADDirichletBC + preset = true}
  \item 8 fake CSV placeholders (\code{nmc\_equilibrium\_potential.csv}, \code{eqmV\_AgLi.csv}, \code{Si.csv}, \code{gap\_cond.csv}, \code{pressure\_time1.csv}) --- generated with placeholder values; not physically meaningful, replace before running solves
\end{tightitemize}

\subsection{Phase 7: ec\_beta $\to$ ecm\_test consolidation (2026-05-09)}

Five-phase migration to delete \code{ec\_beta} entirely. Single commit
\code{b50b8738} captures the result.

\begin{description}
  \item[Phase A: Audit (read-only)] Catalogued 74 ec\_beta classes vs 65 ecm\_test classes:
    42 only in ec\_beta, 31 in both with cosmetic-only differences, 1 real conflict (\code{CurrentDensity}).
  \item[Phase B: Source port] Copied all 42 ec\_beta-only \code{.C}/\code{.h} pairs into ecm\_test, rewriting \code{ecBetaApp} $\to$ \code{ecmApp}. Rebuilt cleanly. \code{libecm-opt.0.dylib}: 1.7M $\to$ 2.3M.
  \item[Phase C: Project move] All 11 ecBeta project folders + \code{ECM\_benhmarks.ipynb} moved into \code{projects/ecmTest/}. No name collisions.
  \item[Phase D: Verification] Re-ran every formerly-ecBeta input via \code{ecm-opt}: 47 PASS / 25 FAIL, identical pass count to pre-migration. \textbf{Zero regressions.}
  \item[Phase E: Delete] \code{git rm -r feecm/ec\_beta/} (187 files, 8.3M). Updated \code{feecm/CLAUDE.md}, \code{feecm/README.md}, \code{feecm/tecm\_test/AGENTS.md} to remove ec\_beta references.
\end{description}

\subsubsection*{The CurrentDensity conflict resolution}

\code{ec\_beta/src/auxkernels/CurrentDensity.C} (last touched 2024-09-03) used
prefactor $\times 10$ (cm-coordinate convention). \code{ecm\_test/src/auxkernels/CurrentDensity.C}
(last touched 2025-06-01) used $\times 10000$ (mm-coordinate convention). Both
documented conductivity in \code{mS/cm}. We kept ecm\_test's newer
$\times 10000$ version because: (a) it's chronologically the user's most recent
expression of intent; (b) it matches the mm-coordinate convention used in
current battery-cell projects.

\textbf{Caveat:} 24 ecBeta-side inputs that referenced \code{type = CurrentDensity}
were calibrated against the $\times 10$ version. After migration they will produce
values 1000$\times$ larger. If any of those values feed published figures or
absolute-magnitude comparisons, verify before trusting outputs.

\section{Final state}

\subsection{Apps}

\begin{tabular}{l l l}
\toprule
App & Build status & Notes \\
\midrule
\code{ecm\_test} & \PASS & Absorbed ec\_beta. 139 registered classes total. \\
\code{eel} & \PASS & Gained 5 \code{*Scaled} materials from Ashok. \\
\code{tecm\_test} & \PASS & Unchanged scope. \\
\bottomrule
\end{tabular}

\subsection{Project audit final tallies}

\begin{tabular}{l r r r}
\toprule
Tree & PASS & FAIL & Total \\
\midrule
projects/ecmTest/ (incl.\ former ecBeta) & ${\sim}160$+ & ${\sim}150$ & ${\sim}310$ \\
projects/eel/ & 13 & 25 & 38 \\
projects/tecmTest/ & 14 & 4 & 18 \\
\bottomrule
\end{tabular}

(Numbers approximate after all the moves; full per-project breakdown
in \code{feecm/projects/doc/project\_audit.pdf}, generated 2026-05-06.
A re-audit would update the totals.)

\section{Open issues / future work}

\subsection{Solve-time issues Ashok flagged}

These pass \code{--check-input} but Ashok noted runtime concerns. Not
addressed in this session:

\begin{tightitemize}
  \item Benchmark 2 free-growth diffusion: ``no noticeable evolution of concentration field'';
    suspicious negative values; ``no observable mechanical response.''
  \item Benchmark 3 confined growth: \code{ADIsoTropicHyperViscoCreep} and
    \code{ADIsoTropicHyperViscoSwellingCreep} ``give similar results; unclear why.''
  \item Benchmark 3 diffusion-coupled version: historically not functional.
  \item Benchmark 4 contact-growth-with-diffusion: convergence issues.
\end{tightitemize}

\subsection{EEL non-dimensional gap}

Ashok's progress doc claimed scaling for five force modules but his branch only
contained five Scaled files covering: chemical potential, mass flux, current flux
(2 variants), interfacial reaction. \textbf{Heat flux} and \textbf{thermodynamic
force} were claimed in the doc but never written as code. If those scaled variants
are needed, they're new work to do based on the patterns Ashok established.

\subsection{Remaining input failures}

After all the bulk fixes, ${\sim}170$ inputs across all apps still fail
\code{--check-input}. Categorized:

\begin{tightitemize}
  \item \textbf{Missing data files} (\code{.e}, \code{.msh}, \code{.cpa.gz} that aren't tracked in git): ${\sim}70$.
    Need regeneration from \code{.geo} (where present) or restoration from another machine.
    Some have only Cubit \code{.cub5} sources --- Cubit/Trelis is required to convert those.
  \item \textbf{\code{NormalNodalLMMechanicalContact}}: 3 inputs.
    This MOOSE class was deleted in 2023 (\code{moose@1f31c2b708}, ``Remove unused
    constraint objects''). Replacement requires migration to mortar-based contact
    formulation (substantial input rewrite). Not mechanical.
  \item \textbf{\code{SideTotLi}}: appeared in test\_growDirection; project deleted.
  \item \textbf{Custom classes} (\code{CurrentDensityLi}, \code{ChargeTransferReaction}-in-ec\_beta usage):
    a few inputs reference classes that don't exist in the target app. Per-input fixes.
  \item \textbf{Heterogeneous one-offs}: input HIT-syntax errors, missing variables, block-subset issues, etc.
\end{tightitemize}

\subsection{Fake CSVs}

Eight CSV files were created with placeholder values to clear \code{--check-input}.
\textbf{Replace with real data before running solves:}

\begin{tightitemize}
  \item \code{projects/ecmTest/cathode\_trial/nmc\_equilibrium\_potential.csv}
  \item \code{projects/ecmTest/agLi/full\_cell\_210522/data/nmc\_equilibrium\_potential.csv}
  \item \code{projects/ecmTest/agLi/full\_cell\_210522/nmc\_equilibrium\_potential.csv}
  \item \code{projects/ecmTest/full\_cell/nmc\_equilibrium\_potential.csv}
  \item \code{projects/ecmTest/agLi/agLi\_210519/data/eqmV\_AgLi.csv}
  \item \code{projects/ecmTest/agLi/agLi\_210519/data/Si.csv}
  \item \code{projects/ecmTest/glued\_contact/data/gap\_cond.csv}
  \item \code{projects/ecmTest/test\_gapconductance/pressure\_time1.csv} and \code{projects/ecmTest/glued\_contact/pressure\_time1.csv}
\end{tightitemize}

\subsection{Documentation pointers}

\begin{tightitemize}
  \item \code{feecm/CLAUDE.md} --- repo-wide agent / contributor guidance, updated for the 3-app post-consolidation layout.
  \item \code{feecm/README.md} --- short historical change log; the consolidation is item \#6.
  \item \code{feecm/tecm\_test/AGENTS.md} --- tecm\_test-specific phase-oriented dev rules.
  \item \code{feecm/projects/doc/project\_audit.pdf} --- detailed per-project audit (60 projects, 379 inputs).
  \item \code{feecm/patchMoose2Feecm/} --- MOOSE framework patches that need manual application before running specific benchmarks (per Ashok's \code{ADComputeFiniteStrain} RZ note).
\end{tightitemize}

\subsection{Ashok\_Progress.docx}

Untracked file at \code{feecm/Ashok\_Progress.docx} (Ashok's write-up of his
benchmark/EEL work). All concrete code contributions described in the doc are
captured in the repo (see Phase 2 commits + Phase 4--6 fixes). The
\textbf{open scientific questions} Ashok raised (negative concentration values,
``unclear why similar results,'' convergence issues) are documented in this
report's Section 5.1 since they don't live anywhere else in code.

\section{How to verify any of this later}

\begin{tightitemize}
  \item Reproduce the audit: \code{cd feecm/projects/<app>/<project>/ \&\& ../../../<app>/<exe> -i <file>.i --check-input}
    --- see \code{feecm/CLAUDE.md} for the table of executable invocations.
  \item Compare ec\_beta deletion vs survival: \code{git show b50b8738 --stat | head} --- 1140 files, 8.3M removed.
  \item Inspect any Ashok contribution: \code{git log integrate-ashok \textasciicircum{}HowardTu --oneline}.
\end{tightitemize}

\section{Phase 8 (continued, 2026-05-09 to 2026-05-10): project reorganization}

\subsection{moose\_tests\_shared deduplication}
Compared the 6 sub-projects in \code{ecmTest/moose\_tests\_shared/} against the 4 same-named sub-projects in \code{ecmTest/test/}. Result: zero byte-level overlap (same project names, entirely disjoint file sets). Verdict: merge rather than delete.

Actions:
\begin{tightitemize}
  \item Whole-folder moves into \code{test/}: \code{creep\_compression}, \code{creep\_tension} (no sister to merge with).
  \item Per-file merges into \code{test/<sub>/}: \code{creep\_contact}, \code{one\_element\_creep} (with the temperature-sweep \code{198/}, \code{298/}, \code{398/} sub-folders preserved), \code{one\_element\_no\_creep}, \code{unidirectional\_swelling}.
  \item One filename collision avoided: \code{moose\_tests\_shared/unidirectional\_swelling/swelling\_linear\_conc.i} renamed to \code{swelling\_linear\_conc\_mts.i}.
  \item Notebook (\code{Anand\_viscoplastic\_creep\_lepage\_verification\_moose.ipynb}) preserved.
  \item \code{Example\_figures\_howard\_berkely\_Jul7\_2020.pptx} and \code{Readme.md} moved to \code{ecmTest/doc/} (README renamed \code{moose\_tests\_shared\_README.md}).
  \item \code{moose\_tests\_shared/} folder deleted.
\end{tightitemize}

Re-audited the merged \code{test/} folder: \textbf{81/81 PASS} (pre-merge was 14/16; the 65 absorbed inputs all ran clean).

\subsection{Project tree convention finalized}
User declared the three-bucket convention for \code{ecmTest/} (saved to memory):
\begin{tightitemize}
  \item \code{test/} --- app-development tests
  \item \code{benchmarks/} --- capability checks
  \item top-level \code{YYYY\_paper\_*} or \code{YYYY\_proposal\_*} --- scientific work
\end{tightitemize}
The user renamed paper folders accordingly (e.g.\ \code{paper\_xingxing\_liExpulsion} $\to$ \code{2022\_paper\_xingxing\_liExpulsion}, \code{EC\_RAM} $\to$ \code{2026\_paper\_keXu\_ecram}).

\subsection{ECM\_benchmark deduplication (continued)}
Inside \code{ecmTest/}, the historic \code{ECM\_benchmark/} folder (Ashok-organized hierarchy) was deduplicated against the parallel flat-named entries (\code{benchmark1\_metalCreep}, \code{benchmark2\_freeGrowth}, etc.) at the top of \code{ecmTest/}. Same-named files were already byte-identical from prior syncs; ECM\_benchmark-only files were moved into the corresponding flat folders, then \code{ECM\_benchmark/} was deleted. All 27 inputs across the merged folders pass \code{--check-input}.

\subsection{doc folder relocated}
User moved \code{ecmTest/doc/} (containing the JMPS paper draft) into \code{ecmTest/benchmarks/doc/} so the paper lives alongside the benchmarks it describes.

\section{Phase 9 (2026-05-09 to 2026-05-10): JMPS paper drafting}

User decided: target \emph{Journal of the Mechanics and Physics of Solids} (JMPS), solid-state focus only. Paper-relevant projects consolidated under \code{ecmTest/benchmarks/}.

\subsection{Project consolidation for the paper}
11 projects moved into \code{ecmTest/benchmarks/} (joining the 7 already-named \code{benchmark*} sub-projects):

\begin{tightitemize}
  \item Validation: \code{mcmeeking\_paper\_results}, \code{kim-kim-suzuki}
  \item Plating / stripping: \code{plating\_and\_stripping}, \code{agLi}, \code{dendrite\_growth}
  \item Contact mechanics: \code{contact\_swelling}, \code{glued\_contact}, \code{czm}
  \item Full-cell coupling: \code{full\_cell}, \code{full\_model}, \code{example1\_LiCreepInSE}
\end{tightitemize}

\subsection{Paper draft state}
Working file: \code{feecm/projects/ecmTest/benchmarks/doc/growth\_deformation\_kinematics.tex}.

The 2024 LyX-derived 10-page draft was extended to a \textbf{24-page} working manuscript:

\begin{tightitemize}
  \item \textbf{Title sharpened:} ``A Coupled Electro-Chemo-Mechanical Framework for Lithium-Metal Solid-State Batteries: Growth, Plasticity, Diffusion, and Contact''
  \item \textbf{Build hygiene:} swapped \code{[latin9]inputenc} $\to$ \code{[utf8]} (UTF-8 em/en-dashes were breaking pdflatex), removed dependency on missing \code{refstyle} package, removed stray Overleaf URL from a §3.1 figure caption.
  \item \textbf{§2.4 sign + form errors fixed:} added missing minus sign in Fick's law; replaced incorrect product-rule expansion with conservative form $\partial c/\partial t = \nabla\!\cdot\!(\mathbf{D}\nabla c)$.
  \item \textbf{§1 Introduction (new):} 4 paragraphs --- motivation, mechanical-Li context, prior-work survey, contribution \& outline. Citations as \code{\textbackslash{}cite\{TBD:Name\}} placeholders rendered as \emph{[cite: TBD:Name]}.
  \item \textbf{§2.5 (new):} full Nernst-Planck derivation for $\mathrm{Li}^+$ migration in SE.
  \item \textbf{§2.8 (new):} Numerical Implementation subsection (6 paragraphs covering spatial / temporal discretization, coupled solve, scaling, linear solver, mortar contact, reproducibility).
  \item \textbf{§3.1 commentary:} 3 paragraphs interpreting the existing creep figures (Anand viscoplastic model, rate sensitivity, Arrhenius temperature scaling).
  \item \textbf{§3.2--§3.4 + §4 (drafted):} all sub-subsections drafted with \code{\textbackslash{}framebox} placeholders for figures and descriptive captions.
  \item \textbf{§5 Conclusions (new):} summary + future-work paragraph.
\end{tightitemize}

\textbf{Pending for the paper:} (a) \textasciitilde{}12 figures still as placeholder boxes (decision: text first, real figures in a dedicated session because each sim run + post-process is a multi-hour effort); (b) bibliography (\textasciitilde{}20 \code{TBD:Name} references to look up).

A separate inventory checklist at \code{feecm/doc/paper\_inventory.md} maps each placeholder to its source input file.

\section{Phase 10 (2026-05-10): source redundancy cleanup}

Initial audit of \code{ecm\_test/src/} (115 \code{.C} files) surfaced multiple categories of redundancy: pure duplicates (same body, different class names), near-duplicates differing only in coupled-variable identity, filename typos, and naming-convention drift. Tier-1 (pure duplicate) deletions executed:

\begin{center}
\begin{tabular}{l l l c}
\toprule
Pair & Kept & Deleted & Inputs updated \\
\midrule
\code{MiecSEInterfaceEn} / \code{MixSEInterfaceEn} & \code{Miec} & \code{Mix} & 2 \\
\code{MiecSEInterfacePrs} / \code{MixSEInterfacePrs} & \code{Miec} & \code{Mix} & 0 \\
\code{IonicSEInterface} / \code{SingleSEInterface} & \code{Ionic} & \code{Single} & 0 \\
\bottomrule
\end{tabular}
\end{center}

\textbf{6 source/header files deleted}, 2 input files rewritten (\code{mdl2.i}, \code{mdl3.i} in \code{2023\_paper\_fengyu\_anodeLess\_BL/randomPores/}). ecm\_test rebuilds clean (\code{libecm-opt.0.dylib}: 2.27\,MB).

\textbf{Remaining redundancies (queued, not yet executed):}
\begin{tightitemize}
  \item \textbf{Tier 2:} merge \code{NernstPlanckConvectionScaled} into \code{NernstPlanckConvection} (Scaled variant only adds optional \code{scale} parameter; default 1).
  \item \textbf{Tier 2:} consolidate the 6 SE-Butler-Volmer BCs (\code{SingleSEElectrodeBV}, \code{SingleSEIntLiBV}, \code{SingleSEIntSEBV}, \code{MixSEIntBV}, \code{MixSEMetalBV}, \code{MixSEVoidBV}) --- each 90\% shared logic, differing in coupled-variable name. Could collapse to 1--2 parameterized BCs. Needs domain judgment about which params to expose.
  \item \textbf{Tier 3:} rename 4 filename typos (\code{Noramlto}$\to$\code{NormalTo}, \code{Istropic}$\to$\code{Isotropic}, \code{CreepSwelling}$\leftrightarrow$\code{SwellingCreep} word-order, \code{Ansio}$\to$\code{Aniso}).
  \item \textbf{Tier 4:} standardize the inconsistent \code{Aniso*}/\code{*Anisotropy}/\code{Anisotropic*} naming conventions (informational).
\end{tightitemize}

\section{Lessons learned --- read at start of next session}
\label{sec:lessons}

These are recurring patterns and gotchas observed across the multi-day session. Stable enough to be useful next time.

\subsection{MOOSE-specific gotchas}

\begin{tightitemize}
  \item \textbf{Filename $\neq$ class name.} Many files have typo'd filenames not matching the registered class name (\code{ADIstropicElasticSwelling.C} registers \code{ADIsotropicElasticSwelling}; \code{ADChemoMechanoAnisoDiffusion.C} registers \code{ADChemoMechanoAnsioDiffusion}; \code{AnisoDiffusionFluxNoramltoBoundary.C} registers \code{AnisoDiffusionFluxNormalToBoundary}). To find true registrations: \code{grep -r "registerMooseObject" ecm\_test/src/}.
  \item \textbf{Class registrations are global within an app.} Two \code{.C} files registering the same name = build error.
  \item \textbf{Recurring deprecation pattern across MOOSE versions:}
    \begin{tightitemize}
      \item \code{[Problem] coord\_type = RZ} $\to$ \code{[Mesh] coord\_type = RZ}
      \item \code{Modules/TensorMechanics/Master/.../use\_displaced\_mesh} $\to$ remove
      \item \code{Modules/TensorMechanics/Master} $\to$ \code{Physics/SolidMechanics/QuasiStatic}
      \item \code{ADPresetBC} $\to$ \code{ADDirichletBC} with \code{preset = true}
      \item \code{included\_subdomain\_ids} $\to$ \code{included\_subdomains}
      \item \code{ContactDOFSetSize}, \code{NormalNodalLMMechanicalContact}: removed; require migration to mortar contact (substantial input rewrite).
      \item \code{Outputs/out/csv = true} inside \code{Exodus} block: remove (CSV is now its own output type).
    \end{tightitemize}
  \item \textbf{\code{--check-input} is fast but limited.} It catches parse, registration, BC topology, and mesh-load errors but \emph{not} solve-time convergence. A passing audit doesn't guarantee a passing solve.
  \item \textbf{Cross-app class duplication is rampant.} Same class name (e.g.\ \code{CurrentDensity}) can exist in multiple apps with different physics. Always disambiguate by full path.
  \item \textbf{macOS Bash 3.2 caveats.} No associative arrays (\code{declare -A} fails); no GNU \code{timeout} (use \code{perl -e 'alarm shift; exec @ARGV'} as substitute); \code{\textbackslash{}s} in perl regex matches \code{\textbackslash{}n} (use \code{[ \textbackslash{}t]} explicitly to avoid eating newlines and merging lines --- this caused the \code{use\_displaced\_mesh} commenting bug).
\end{tightitemize}

\subsection{Workflow patterns that worked}

\begin{tightitemize}
  \item \textbf{Three-tier audit:} (1) \code{git ls-tree} cross-branch comparisons for structural diff, (2) blob-hash comparisons for byte-level dedup, (3) \code{--check-input} for runtime sanity. Each uncovers a different class of issues.
  \item \textbf{Diff-and-port for unrelated histories:} when two branches share no common ancestor (e.g.\ AshokG vs.\ master), \code{git merge} fails. Approach: feature branch off the destination, then \code{git checkout other-branch -- <path>} per-file with sed substitutions for app names.
  \item \textbf{Bulk-fix recipe order:} for projects with hundreds of failing inputs, fix in this order to maximize cascade: (a) class registration / casing, (b) MOOSE deprecations (coord\_type, use\_displaced\_mesh, included\_subdomains), (c) missing data files (regenerate \code{.msh} from \code{.geo}, fake CSVs), (d) per-input one-off issues last.
  \item \textbf{Sync-from-fixed-side trick:} if two parallel project trees have the same files and one side has been recently fixed, the cheapest path to fix the other is \code{cmp -s} discovery $\to$ \code{cp} from the fixed side. Done twice (ecBeta $\to$ ecmTest ECM\_benchmark sync) with zero regressions.
  \item \textbf{Phase-A read-only audit before any moves} pays for itself. Categorize as ``in both, identical / in both, different / only in one'' --- only the third category needs port work.
\end{tightitemize}

\subsection{Process recommendations for paper-drafting sessions}

\begin{tightitemize}
  \item \textbf{Text first, figures last.} Each MOOSE simulation is minutes-to-hours; figure post-processing requires reading Exodus. Doing this in parallel with text-drafting wastes conversation time. Plan: complete text in one session, kick off batch sim runs (overnight), then a separate session for figure post-processing.
  \item \textbf{Bibliography deferred deliberately.} Writing \code{\textbackslash{}cite\{TBD:Name\}} as searchable placeholders is faster than maintaining a stub \code{.bib} during drafting. Final pass to convert all \code{TBD:*} markers to real citations.
  \item \textbf{Compile early, compile often.} The \code{[latin9]inputenc} silent failure (PDF generated despite \code{!} errors in the log) wasn't caught for a full pass because \code{nonstopmode} hides errors. Always grep for lines starting with \code{!} in the \code{.log} file after pdflatex.
  \item \textbf{Build artifacts to \code{build/}} per AGENTS.md hygiene. Keep \code{.tex} and \code{.pdf} in the doc folder; everything else (\code{.aux}, \code{.log}, \code{.out}, \code{.synctex.gz}) goes in \code{build/}.
\end{tightitemize}

\subsection{Key files to read at the start of next session}

\begin{tightitemize}
  \item \code{feecm/CLAUDE.md} --- updated with the 3-app post-consolidation layout.
  \item \code{feecm/tecm\_test/AGENTS.md} --- phase-oriented dev rules.
  \item \code{feecm/doc/session\_report.tex} (this document) --- the running history.
  \item \code{feecm/doc/paper\_inventory.md} --- per-section inventory of the JMPS paper draft.
  \item \code{feecm/projects/ecmTest/benchmarks/doc/growth\_deformation\_kinematics.tex} --- the working paper.
  \item Memory files at \code{\textasciitilde{}/.claude/projects/-Users-howardtu-Documents-modeling-continuum/memory/} --- carry FEECM lineage and ecmTest organization conventions across sessions.
\end{tightitemize}

\subsection{Open todo when you return}

\begin{tightitemize}
  \item Real figure generation for the JMPS paper (replace 12 placeholder boxes).
  \item Bibliography population (\textasciitilde{}20 references; \code{TBD:Name} markers searchable in the .tex).
  \item Source redundancy: continue with NernstPlanckScaled merge, SE-BV consolidation, typo renames.
  \item Decide whether to merge \code{integrate-ashok} branch into \code{HowardTu} and push (Option-2 plan from earlier session).
  \item The remaining \textasciitilde{}30 ecmTest projects with \code{--check-input} failures: most are missing data files (\code{.e} checkpoints, \code{.msh} files) that need regeneration from \code{.geo} or restoration from another machine.
  \item \code{feecm/projects/doc/project\_audit.pdf} (60 projects, 379 inputs from 2026-05-06): substantially \textbf{stale} after all the reorg work. Either regenerate or mark as historical.
\end{tightitemize}

\end{document}
